
We are convinced that our model provides an accurate estimate of where the meeting should take place. It not only considers the most influential factors but also fairly subtle elements such as noise and light pollution. While being precise it likewise comes with a number of perks:  

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
\item[+] It is fast. The algorithm we use is linear to the number of places considered.  
\item[+] It is stable. For a set of inputs it always gives the same output.
\item[+] It is easy to customize. Using the parameters we can easily alter the sub-models in accordance with attendant preferences and further research.
\item[+] It is guaranteed that the algorithm finds the best solution possible, as opposed to algorithms which may only find one of the best solutions or their behavior is based on probabilities.
\item[+] Addition of extra sub-models is simple.
\item[+] Certain factors can be easily omitted based on attendant inclinations.
\item[+] The extent to which cost is a secondary criterion depends on the organizing committee.  
\end{itemize}

While we believe in the correctness of our model, there is always room for improvement. We are considering the following points as weaknesses and thus possibilities for future development:

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
\item[--] Our model is restricted to a set number of cities. While we believe we have justified the reasoning behind this decision we consider an algorithm which is able to effectively map any point on the earth with respect to various factors superior.
\item[--] We had to estimate data. Due to lack of data, we had to do estimations which decreased the credibility of our model.
\item[--] The vast number of parameters makes it harder for organizers to correctly tailor each sub-model.
\item[--] There is no implemented way of automatically processing attendant feedback and in this way developing the model.
\end{itemize}

The future of our model can be broken down into major three parts. Firstly, we need to find more and better data. Secondly, we shall improve the sub-models and make them easier to modify by the organizers. Finally, we should design a uniform and effective way of receiving information from the attendees directly about their preferences and implement an automated way of evaluating it, possibly with the use of machine learning algorithms, to assess attendant feedback.


